Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-02-27 presentation-plan/Plan_presentation_monday.tex
Add some extra limitations of STRIP

\begin{itemize}
	\item How to efficiently store nodes (states) of the world.~\cite{fikes1971strips}.
	\item ...
\end{itemize}

>>>>

\begin{itemize}
	\item How to efficiently store nodes (states) of the
		world.~\cite{fikes1971strips}
	\item Arbitrary STRIPS planning problem is a PSPACE complete
		problem.~\cite{mcallester1991systematic}
	\item Extremely limited in scope of planning problems and complexity of
		problems it can solve.~\cite{fikes1994strips}
\end{itemize}
